OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2017-11-23 supplementary_figures_nar.tex
Edited legends of supplementary figures.

\begin{figure}[b]
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_1.eps}}
	\caption{
    Pearson correlation between contact profiles and independent copy number
	estimation (COSMIC). A. T47D breast cancer cell line (6 samples). B. K562
	leukemia cell line (8 samples). Each dot represents a sample. The new
	proposal (in dark blue) outperforms the rest of alternatives.}
\end{figure}

@@

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_3.eps}}
    \caption{
    Distribution of the pair-wise comparisons between the samples included in
    the K562 set. X axis: similarity metric. Y axis: correction
    method. Each panel groups pairs of samples with the corresponding
    characteristics (in terms of cell type and protocol). A. Pearson correlation
    between observed over expected counts. B. Spearman correlation between
    observed counts. C. Stratum-adjusted correlation coefficient (SCC) between
    observed counts. D. Reproducibility score of observed counts.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_4.eps}}
    \caption{
    Removing biases from Hi-C on aberrant karyotypes (Spearman correlation). A and B. Average changes
    compared to the raw data on the T47D and K562 data sets. The bars represent
    95\% confidence intervals centered on the mean difference of the
    spearman correlation between a given correction method and the raw data. C
    and D. ROC curves on the T47D and K562 sets. The areas under the curve are
    indicated in the bottom right corner. The color code is the same as in panels A and B.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_5.eps}}
    \caption{
    Removing biases from Hi-C on aberrant karyotypes (Pearson correlation). A and B. Average changes
    compared to the raw data on the T47D and K562 data sets. The bars represent
    95\% confidence intervals centered on the mean difference of the
    Pearson correlation of the observed over expected between a given correction method and the raw data. C
    and D. ROC curves on the T47D and K562 sets. The areas under the curve are
    indicated in the bottom right corner. The color code is the same as in panels A and B.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_6.eps}}
    \caption{
    Removing biases from Hi-C on aberrant karyotypes (SCC). A and B. Average changes
    compared to the raw data on the T47D and K562 data sets. The bars represent
    95\% confidence intervals centered on the mean difference of the
    stratum-adjusted correlation coefficient (SCC) between a given correction method and the raw data. C
    and D. ROC curves on the T47D and K562 sets. The areas under the curve are
    indicated in the bottom right corner. The color code is the same as in panels A and B.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_7.eps}}
    \caption{
    Distribution of the pair-wise comparisons between the samples included in
    the mm10 set. X axis: similarity metric. Y axis: correction
    method. Each panel groups pairs of samples with the corresponding
    characteristics (in terms of cell type and protocol). A. Pearson correlation
    between observed over expected counts. B. Spearman correlation between
    observed counts. C. Stratum-adjusted correlation coefficient (SCC) between
    observed counts. D. Reproducibility score of observed counts.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_8.eps}}
    \caption{
    Removing biases from Hi-C on normal karyotypes (Spearman correlation). A. Average changes
    compared to the raw data on the mm10 data set. The bars represent
    95\% confidence intervals centered on the mean difference of the
    Spearman correlation between a given correction method and the raw
    data. B. ROC curves on the mm10 set. The areas under the curve are indicated
    in the bottom right corner. The color code is the same as in panel A.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_9.eps}}
    \caption{
    Removing biases from Hi-C on normal karyotypes (Pearson correlation). A. Average changes
    compared to the raw data on the mm10 data set. The bars represent
    95\% confidence intervals centered on the mean difference of the
    Pearson correlation of the observed over expected correlation between a given correction method and the raw
    data. B. ROC curves on the mm10 set. The areas under the curve are indicated
    in the bottom right corner. The color code is the same as in panel A.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_10.eps}}
    \caption{
    Removing biases from Hi-C on normal karyotypes (SCC). A. Average changes
    compared to the raw data on the mm10 data set. The bars represent
    95\% confidence intervals centered on the mean difference of the
    stratum-adjusted correlation coefficient (SCC) between a given correction method and the raw
    data. B. ROC curves on the mm10 set. The areas under the curve are indicated
    in the bottom right corner. The color code is the same as in panel A.}
\end{figure}

>>>>

\begin{figure}[b]
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_1.eps}}
  \caption{ Pearson correlation between contact profiles and independent
copy number estimation from the COSMIC data base (Forbes \textit{et al}.,
2010). A. T47D breast cancer cell line (6 samples). B. K562 leukemia cell
line (8 samples). Each dot represents a sample normalized by a different
tool. The data normalized by \textit{OneD} correlates better with the copy
number than the unnormalized data.}
\end{figure}

@@

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_3.eps}}
  \caption{Distribution of the pair-wise comparisons between the
samples included in the K562 set. X axis: similarity metric. Y axis:
correction method. Each panel groups pairs of samples with the
corresponding characteristics (in terms of cell type and protocol). A.
Pearson correlation between observed over expected counts. B. Spearman
correlation between observed counts. C. Stratum-adjusted correlation
coefficient (SCC) between observed counts. D. Reproducibility score of
observed counts.} \end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_4.eps}}
    \caption{Removing biases from Hi-C on aberrant karyotypes (Spearman
correlation). A and B. Average changes compared to the raw data on the
T47D and K562 data sets. The bars represent 95\% confidence intervals
centered on the mean difference of the Spearman correlation between a
given correction method and the raw data. C and D. ROC curves on the T47D
and K562 sets. The areas under the curve are indicated in the bottom right
corner. The color code is the same as in panels A and B.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_5.eps}}
  \caption{Removing biases from Hi-C on aberrant karyotypes (Pearson
correlation). A and B. Average changes compared to the raw data on the
T47D and K562 data sets. The bars represent 95\% confidence intervals
centered on the mean difference of the Pearson correlation of the observed
over expected counts between a given correction method and the raw data. C
and D. ROC curves on the T47D and K562 sets. The areas under the curve are
indicated in the bottom right corner. The color code is the same as in
panels A and B.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_6.eps}}
  \caption{Removing biases from Hi-C on aberrant karyotypes (SCC). A and
B. Average changes compared to the raw data on the T47D and K562 data
sets. The bars represent 95\% confidence intervals centered on the mean
difference of the stratum-adjusted correlation coefficient (SCC) between a
given correction method and the raw data. C and D. ROC curves on the T47D
and K562 sets. The areas under the curve are indicated in the bottom right
corner. The color code is the same as in panels A and B.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_7.eps}}
  \caption{Distribution of the pair-wise comparisons between the samples
included in the mm10 data set. X axis: similarity metric. Y axis:
correction method. Each panel groups pairs of samples with the
corresponding characteristics (in terms of cell type and protocol). A.
Pearson correlation between observed over expected counts. B. Spearman
correlation between observed counts. C. Stratum-adjusted correlation
coefficient (SCC) between observed counts. D. Reproducibility score of
observed counts.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_8.eps}}
  \caption{Removing biases from Hi-C on normal karyotypes (Spearman
correlation). A. Average changes compared to the raw data on the mm10 data
set. The bars represent 95\% confidence intervals centered on the mean
difference of the Spearman correlation between a given correction method
and the raw data. B. ROC curves on the mm10 data set. The areas under the
curve are indicated in the bottom right corner. The color code is the same
as in panel A.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_9.eps}}
  \caption{Removing biases from Hi-C on normal karyotypes (Pearson
correlation). A. Average changes compared to the raw data on the mm10 data
set. The bars represent 95\% confidence intervals centered on the mean
difference of the Pearson correlation of the observed over expected counts
between a given correction method and the raw data. B. ROC curves on the
mm10 data set. The areas under the curve are indicated in the bottom right
corner. The color code is the same as in panel A.}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=\textwidth]{nar_figures/supp_figure_10.eps}}
  \caption{Removing biases from Hi-C on normal karyotypes (SCC). A.
Average changes compared to the raw data on the mm10 data set. The bars
represent 95\% confidence intervals centered on the mean difference of the
stratum-adjusted correlation coefficient (SCC) between a given correction
method and the raw data. B. ROC curves on the mm10 data set. The areas
under the curve are indicated in the bottom right corner. The color code
is the same as in panel A.}
\end{figure}
